Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-05 causal-bandit/icml-2015/discussion.tex
Note on unknown graph

\paragraph{Causal Models with Non-Observable Variables}
We have assumed through this paper that all variables in the causal model were observable after an intervention is made.
A natural generalisation of our model would be for some variables to be unobservable.
\todom{More to say here?}
If the conditional models are known then the $Z_a$ terms in Algorithm~\ref{alg:general} could still be obtained via marginalising.
However, if this is not the case the estimation problem becomes more difficult.
% In this case, some conditional distributions may be non-identifiable. 
% The corresponding actions can be immediately added to the set $A$ prior to collecting any data. 
% We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data.
Combining our estimation techniques with insights from \citet{Bareinboim2015} for handling unobserved confounders would be worth investigation.

@@

\paragraph{Partially or Completely Unknown Causal Graph}
A much more difficult generalisation would be to consider causal bandit problems where the causal graph is completely unknown or known to be a member of class of models.
The latter case arises naturally if we assume free access to a large observational dataset, from which the Markov equivalence class can be found via causal discovery techniques. 
Work on the problem of selecting experiments to discover the correct causal graph from within a Markov equivalence class~\cite{Eberhardt2005,eberhardt2010causal,hauser2014two,Hu2014} could potentially be incorporated into a causal bandit algorithm as part of a pre-processing step.
Simultaneously learning a completely unknown causal model while estimating the rewards of interventions would be much more challenging.
\citet{Hu2014b} show that ...

>>>>

\paragraph{Causal Models with Non-Observable Variables}
We have assumed through this paper that all variables in the causal model were observable after an intervention is made.
A natural generalisation of our model would be for some variables to be unobservable.
\todom{More to say here?}
If the conditional models are known then the $Z_a$ terms in Algorithm~\ref{alg:general} could still be obtained via marginalising.
However, if this is not the case the estimation problem becomes more difficult.
% In this case, some conditional distributions may be non-identifiable. 
% The corresponding actions can be immediately added to the set $A$ prior to collecting any data. 
% We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data.
% Combining our estimation techniques with insights from \citet{Bareinboim2015} for handling unobserved confounders would be worth investigation.

@@

\paragraph{Partially or Completely Unknown Causal Graph}
A much more difficult generalisation would be to consider causal bandit problems where the causal graph is completely unknown or known to be a member of class of models.
The latter case arises naturally if we assume free access to a large observational dataset, from which the Markov equivalence class can be found via causal discovery techniques. 
Work on the problem of selecting experiments to discover the correct causal graph from within a Markov equivalence class~\cite{Eberhardt2005,eberhardt2010causal,hauser2014two,Hu2014b} could potentially be incorporated into a causal bandit algorithm.
In particular, \citet{Hu2014b} show that only $\bigo{\log \log n}$ multi-variable interventions are required on average to recover a causal graph over $n$ variables once purely observational data is used to recover the ``essential graph''.
Simultaneously learning a completely unknown causal model while estimating the rewards of interventions without a large observational dataset would be much more challenging.
